Accounting for uncertainty in simulation greenhouse gas emissions from dairy cattle in Kenya

### 2022-06-02 Manuscript_analyses.Rmd
cleaned up and reformated html

---
title: "Accounting for uncertainty in simulation greenhouse gas emissions from dairy cattle in Kenya"
author: "Eike Luedeling, Cory Whitney, Todd Rosenstock"
bibliography:
 - references/packages.bib
 - references/papers.bib
output:
  html_document:
    theme: united
    toc: true
    toc_float: true
    number_sections: true
---

@@

```{r plot_distributions, fig.width=10, fig.height=10}
# enteric_CH4=enteric_CH4,
enteric_CH4_dist_plot <- plot_distributions(mcSimulation_object = GHG_simulation_scenarios,
                   vars = "enteric_CH4",
                   method = "boxplot_density",
                   old_names = "enteric_CH4",
                   new_names = "CH[4]~Emissions~from~Enteric~Fermentation~(kg~CH[4])") + 
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank())

@@

```{r varkernelslicerange}
slice<-uncertainty::varslice_resample(in_var = dairy_households$y$pc_milk_yield,
                                 out_var = dairy_households$y$CO2eq_per_milk, 
                                 expectedin_var=2000,
                           n = 1000,
                           n_samples = 1000,
                           out_var_sampling = 1000)

@@

Let's look at this for production of 2000 and 3000 kg milk per capita per year. We'll take 1000 random draws of the emissions intensities that associated with both levels and compare values among these samples.

@@

sum(slice_3000$resampled < slice_2000$resampled) / length(slice_2000$resampled)

@@

```{r}
cows<-Kenyaherds[which(Kenyaherds$animal_type %in% 4:6),]

@@

```{r}
breed_res$y[,"CO2eq_per_milk"]<-breed_res$y$pc_on_farm/breed_res$y$pc_milk_yield

@@

```{r, message=FALSE, warning=FALSE}

@@

```{r}
nobull_res$y[,"CO2eq_per_milk"]<-nobull_res$y$pc_on_farm/nobull_res$y$pc_milk_yield

@@

>>>>

---
title: "Accounting for uncertainty in simulation greenhouse gas emissions from dairy cattle in Kenya"
author: "Eike Luedeling, Cory Whitney, Todd Rosenstock"
bibliography:
 - references/packages.bib
 - references/papers.bib
output:
  html_document:
    theme: united
    toc: true
    toc_float: true
    number_sections: true
    code_folding: hide
---

@@

```{r plot_distributions, fig.width=10, fig.height=10, message=FALSE, warning=FALSE}
# enteric_CH4=enteric_CH4,
enteric_CH4_dist_plot <- plot_distributions(mcSimulation_object = GHG_simulation_scenarios,
                   vars = "enteric_CH4",
                   method = "boxplot_density",
                   old_names = "enteric_CH4",
                   new_names = "CH[4]~Emissions~from~Enteric~Fermentation~(kg~CH[4])") + 
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank())

@@

```{r varkernelslicerange, message=FALSE, warning=FALSE}
slice<-uncertainty::varslice_resample(in_var = dairy_households$y$pc_milk_yield,
                                 out_var = dairy_households$y$CO2eq_per_milk, 
                                 expectedin_var=2000,
                           n = 1000,
                           n_samples = 1000,
                           out_var_sampling = 1000)

@@

Let's look at this for production of 2000 and 3000 kg milk per capita per year. We'll take 1000 random draws of the emissions intensities that are associated with both levels and compare values among these samples.

@@

# sum(slice_3000$resampled < slice_2000$resampled) / length(slice_2000$resampled)

@@

```{r, warning=FALSE}
cows<-Kenyaherds[which(Kenyaherds$animal_type %in% 4:6),]

@@

```{r, fig.dim = c(8, 8)}
breed_res$y[,"CO2eq_per_milk"]<-breed_res$y$pc_on_farm/breed_res$y$pc_milk_yield

@@

```{r, message=FALSE, warning=FALSE, fig.dim = c(8, 8)}

@@

```{r, fig.dim = c(8, 8)}
nobull_res$y[,"CO2eq_per_milk"]<-nobull_res$y$pc_on_farm/nobull_res$y$pc_milk_yield

@@

```{r, fig.dim = c(8, 8)}
